random forest and lme

### 2020-04-11 src/modelling - 550/rf.Rmd
shiny app update

```{r}
dat <- readr::read_delim("test_train_data.txt", delim = ",", col_types = "ciccdddddc")
train <- readr::read_delim("train_data.txt", delim = ",", col_types = "ciccddddd")
test <- readr::read_delim("test_data.txt", delim = ",", col_types = "ciccddddd")
dat$municipality <- as.factor(dat$municipality)

>>>>

```{r}
dat <- readr::read_delim("test_train_data.txt", delim = ",", col_types = "ciccdddddc")
dat$municipality <- as.factor(dat$municipality)
